Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimization Choices

### 2025-11-20 revision/response.qmd

7. I was also wondering how the dependence of the smoothness on d can be explained, since it is not intuitive that this should change so much? (Note also that the last sentence in the caption for Table 1 seems to mix up squintability and smoothness.)

\textcolor{blue}{Table 1 is a subset of the PP index estimated and it happens that the three chosen ones all decrease as $n$ goes larger. This is not necessary the case in the full table shown in the Appendix. The caption for Table 1 has been fixed.}

8. Finally, I appreciate the practical advice in section 7. Here, 7.1 should be somewhat extended in my opinion: does the planned tour then run through all the individual paths, should we follow the most successful jellyfish, or how would we pick?

\textcolor{blue}{We make Section 7.1 clearer that the planned tour can be run to trace the optimisation of individual jellyfish path. Users may wish to follow the most successful jellyfish, a random selection, or interesting jellyfish that result in local optimum.}

### 2025-11-20 jso.qmd
link to examples in search_jellyfish

To use JSO for PPGT in the `tourr` package, specify
`search_f = search_jellyfish` in the guided tour. 
The animation function `animate_*()` won't directly render the animated 
projection for JSO, as with other existing optimizers since multiple tour 
paths will need to be generated. To
visualize the path visited by each individual jellyfish, assign the
animation to an object (`res <- animate_xy(...)`). This will save all the
bases visited by JSO, along with relevant metadata, as a tibble data
object [see @RJ-2021-105 for more details on the data object]. Users can 
then view the path of individual jellyfish through extracting the relevant 
bases recorded and construct it as a planned tour (using the `planned_tour()` function).
Users may wish to view the 
optimisation path of the most successful jellyfish, or a random selection of jellyfish, 
or some specific runs that find local maximum.

>>>>

To use JSO for PPGT in the `tourr` package, specify
`search_f = search_jellyfish` in the guided tour. 
The animation function `animate_*()` won't directly render the animated 
projection for JSO, as with other existing optimizers since multiple tour 
paths will need to be generated. To
visualize the path visited by each individual jellyfish, assign the
animation to an object (`res <- animate_xy(...)`). This will save all the
bases visited by JSO, along with relevant metadata, as a tibble data
object [see @RJ-2021-105 for more details on the data object]. Users can 
then view the path of individual jellyfish through extracting the relevant 
bases recorded and construct it as a planned tour using the `planned_tour()` function (see the examples via `?search_jellyfish`).
Users may wish to view the 
optimisation path of the most successful jellyfish, or a random selection of jellyfish, 
or some specific runs that find local maximum.

### 2025-11-20 jso.tex
link to examples in search_jellyfish

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, titlerule=0mm, opacitybacktitle=0.6, left=2mm, toprule=.15mm, colback=white, leftrule=.75mm, arc=.35mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, breakable, title={Algorithm: Jellyfish Optimizer Pseudo Code}, bottomtitle=1mm, rightrule=.15mm, bottomrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, opacityback=0]

@@

To use JSO for PPGT in the \texttt{tourr} package, specify
\texttt{search\_f\ =\ search\_jellyfish} in the guided tour. The
animation function \texttt{animate\_*()} won't directly render the
animated projection for JSO, as with other existing optimizers since
multiple tour paths will need to be generated. To visualize the path
visited by each individual jellyfish, assign the animation to an object
(\texttt{res\ \textless{}-\ animate\_xy(...)}). This will save all the
bases visited by JSO, along with relevant metadata, as a tibble data
object (see Zhang et al. 2021 for more details on the data object).
Users can then view the path of individual jellyfish through extracting
the relevant bases recorded and construct it as a planned tour (using
the \texttt{planned\_tour()} function). Users may wish to view the
optimisation path of the most successful jellyfish, or a random
selection of jellyfish, or some specific runs that find local maximum.

>>>>

\begin{tcolorbox}[enhanced jigsaw, left=2mm, breakable, coltitle=black, colframe=quarto-callout-note-color-frame, title={Algorithm: Jellyfish Optimizer Pseudo Code}, opacityback=0, colback=white, leftrule=.75mm, bottomrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, bottomtitle=1mm, arc=.35mm, toptitle=1mm, titlerule=0mm, rightrule=.15mm, toprule=.15mm, opacitybacktitle=0.6]

@@

To use JSO for PPGT in the \texttt{tourr} package, specify
\texttt{search\_f\ =\ search\_jellyfish} in the guided tour. The
animation function \texttt{animate\_*()} won't directly render the
animated projection for JSO, as with other existing optimizers since
multiple tour paths will need to be generated. To visualize the path
visited by each individual jellyfish, assign the animation to an object
(\texttt{res\ \textless{}-\ animate\_xy(...)}). This will save all the
bases visited by JSO, along with relevant metadata, as a tibble data
object (see Zhang et al. 2021 for more details on the data object).
Users can then view the path of individual jellyfish through extracting
the relevant bases recorded and construct it as a planned tour using the
\texttt{planned\_tour()} function (see the examples via
\texttt{?search\_jellyfish}). Users may wish to view the optimisation
path of the most successful jellyfish, or a random selection of
jellyfish, or some specific runs that find local maximum.
